\documentclass{res} 			% LaTeX resume using res.cls
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage[none]{hyphenat}		% no hyphenation patterns exist
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  			% use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Donglei ZHANG} % force lhead all the way left
\rhead{Page \thepage}  			% put page number at right
\cfoot{}  						% the footer is empty
\pagestyle{fancy} 				% set pagestyle for the document
\setmainfont{Palatino Linotype} % set custom font

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{Donglei ZHANG\ {\fontspec{KaiTi} (张栋磊)}}
\address{ \vspace{0.2in} \\
  Room 940, Cheng Yu Tung Building, \\
  No. 12 Chak Cheung Street,\\
  Shatin, N.T., Hong Kong SAR} 
\address{ \vspace{0.2in} \\
  Tel: +852 3943 9296 \\
  Email: zhangdonglei@link.cuhk.edu.hk \\
  http://dongleizhang.com \\}

\begin{resume} 
\vspace{0.1in}

\section{RESEARCH INTERESTS}
\vspace{0.1in}
	Applied Microeconometrics, Behavior Economics


\section{EDUCATION}
\vspace{0.1in} 
    {\bf The Chinese University of Hong Kong (CUHK)}, Hong Kong \\
    {\sl Ph.D. student in Decision Sciences and Managerial Economics, Aug. 2016 - Present} \\
    Advisors: Prof. Xiaoquan (Michael) Zhang, Prof. Xiaoyu Xia
    
    {\bf The Hong Kong University of Science and Technology (HKUST)}, Hong Kong \\
    {\sl M.Sc. in Economics, 2016} 

    {\bf Zhejiang University (ZJU)}, Hangzhou, China \\
    {\sl B.A. in Economics, Experimental Class of Economics, 2015}


\section{PROFESSIONAL EXPERIENCE} 
\vspace{0.1in} 
    {\bf Teaching Assistant}, 
    Department of Decision Sciences and Managerial Economics,
    CUHK Business School, Hong Kong,
    Aug. 2016 - Present \\
    DSME2011: Statistical Analysis for Business Decisions, 2017/18 \\
    DSME2021: Applied Econometrics for Business Decisions, 2016/17 \\
    DSME1030: Economics for Business Studies I, 2016/17
    
    {\bf Research Assistant},
    Department of Economics,
    The Hong Kong University of Science and Technology, Hong Kong,
    Nov. 2015 - Jun. 2016 \\
    Supervisor: Prof. Yao (Amber) Li
    
    {\bf Summer Internship}, 
    Huatai Securities, Hangzhou, China, 
    Jul. 2014 - Aug. 2014
    

\section{WORKING PAPERS} 
\vspace{0.1in}
	``{\bf \href{http://dongleizhang.com/file/zju_thesis.pdf}{Macroeconomic Regulations and Adjustment Speed of Listed Real Estate Companies' Capital Structure}}'', {\sl Undergraduate thesis}, 2015. \\
		This thesis studies China’s real estate companies’ capital structure adjustment behavior in the aspect of macroeconomic regulations. The study finds that the adjustment speed is higher under stimulating policy. Both stimulating and restraining policies can affect the short-term debt financing, and internal retained earnings are the fastest option to optimize capital structures, but the mixed path is the most efficient option.

	``{\bf \href{http://dongleizhang.com/file/labor_migration.pdf}{Dependence of Labor Migration Decision-Making in China's Urbanization}}'' (in Chinese), with Birong Yang and Yong You, {\sl ZJU research project}, 2015. \\
		The study tries to clarify how much does labor migration decision-making depend on social interaction between individuals. After analyzing CHIPs data with a Probit model, we find that peer effects exist in the decision-making of labor migration. The influence of peer effects on individual migration decision-making connects with the social interaction between individuals and other members of the community.


\section{WORK IN PROGRESS}
\vspace{0.1in}
	``Online Targeted Advertising on Social Media'', {\sl CUHK working paper}.
	
	``Fake News, Media Bias, and Purchase Decision'', {\sl CUHK working paper}.


\section{PRESENTATIONS} 
\vspace{0.1in}
	The 7\textsuperscript{th} International Research Exchange and Faculty Development Conference, Apr. 2017


\section{SELECTED AWARDS \& RESEARCH GRANTS} 
\vspace{0.1in}
   Postgraduate Studentship, The Chinese University of Hong Kong, 2016 - 2020
   
   Second Prize, 14\textsuperscript{th} Zhejiang Province Challenge Cup Academic Works Competition, 2015
   
   Grant from Xinmiao Talent Program (2014R401002), Department of Education, Zhejiang Province, China, 2014
   
   Grant from Student Research Training Program, Zhejiang University, 2013
   
   Second-Class Scholarship for Excellence in Research and Innovation, Zhejiang University, Year 2012/13
   
   Second Prize, 13\textsuperscript{th} Zhejiang Province Challenge Cup Academic Works Competition, 2013
   
   Excellent Student Award, Zhejiang University, Year 2011/12
   
   Third-Class Scholarship for Outstanding Students, Zhejiang University, Year 2011/12


\section{SKILLS \& QUALIFICATION} 
\vspace{0.1in}
   Language: Chinese Mandarin (native), English (fluent)

   Computer skills: \LaTeX, Stata, Matlab, Eviews
   
   Qualification: Securities Practice Qualification of China


\end{resume}

\vspace{0.5in}
\leftskip=15em Last updated: \today

\end{document}